# Posterior Predictive Checks Model-AR: Public Goods Game

```{r}
install.packages("pacman")
set.seed(42)
pacman::p_load(R2jags, parallel, polspline, tidyverse, ggplot2, bayesplot)
setwd("/work/LauraGivskovRahbek#6659/decision_making_exam24/src/model_AR")
source("../utils.R")
```

## Parameter Estimation (Per Group)
### Load data and vars
Each Combination of Sect and Treatment (6 groups)

```{r}
load("../../out/EstData/est_vars_AR.RData") 
samp_names <- paste0("samp", SeTr)
for (i in 1:length(file_names)){
  load(file_names[[i]])
  assign(paste0(samp_names[i]), samples)
}
samples_ls <- list("sampC_0" = sampC_0, "sampC_1" = sampC_1, "sampS_0" = sampS_0, 
                   "sampS_1" = sampS_1, "sampSh_0" = sampSh_0, "sampSh_1" = sampSh_1)
param_names <- c("mu_alpha", "mu_rho", "sigma_alpha", "sigma_rho")
```

### Estimated Parameters

```{r}
estimated_parameters <- array(NA, dim = c(length(param_names), length(samples_ls)), 
                              dimnames = list(c(param_names), c(names(samples_ls))))
for (p in param_names){
  for (s in 1:length(samples_ls)){
    estimated_parameters[p, s] <- MPD(samples_ls[[s]]$BUGSoutput$sims.list[[p]])
  }
}
estimated_parameters
```

### Prior distributions for SECTxTREATMENT
```{r}
pdf(file = "../../out/prior_distributions.pdf")
par(mfrow = c(2,2))
plot(density(rgamma(1000, 2.6, 0.4)), main = "Prior: Mu Alpha")
abline(v = c(0.001, 10), col = "red")
plot(density(rnorm(1000, 1, 2)),  xlim = c(-2, 5), main = "Prior: Sigma Alpha")
abline(v = c(0.001), col = "red")
plot(density(rbeta(1000, 1, 1)), main = "Prior: Mu Rho")
abline(v = c(0,1), col = "red")
plot(density(runif(1000, 10, 100)),  main = "Prior: Sigma Rho")
abline(v = c(10, 100), col = "red")
dev.off()
```


### Posterior Distributions for SECTxTREATMENT 

```{r}
pdf(file = "../../out/AR_est_posterior.pdf")
par(mfrow = c(3,3))
for (p in param_names){
  for (s in 1:length(samples_ls)){
    plot(density(samples_ls[[s]]$BUGSoutput$sims.list[[p]]), 
         main = paste(p, samp_names[s], sep = " - ") )
  }
}
dev.off()
```


### Summary Tables (SECTxTREATMENT)
```{r}
print("Christian same-sect")
sampC_0
print("Christian mixed-sect")
sampC_1
print("Sunni same-sect")
sampS_0
print("Sunni same-sect")
sampS_1
print("Shia same-sect")
sampSh_0
print("Shia same-sect")
print(sampSh_1)

#save to folder
folder_path <- "../../out/posterior_dist_summaries/m_AR_est_"
for (i in 1:length(samples_ls)){
  path <- str_c(folder_path, sprintf("%s.csv", SeTr[i]))
  write.csv((samples_ls[[i]]$BUGSoutput$summary), file = path)
}
```

### Traceplots
```{r}
folder_path <-  "../../out/traceplots/m_AR_est_"

for (i in 1:length(samples_ls)){
  path <- str_c(folder_path, sprintf("%s.pdf", SeTr[i]))
  pdf(file = path)
  traceplot(samples_ls[[i]], ask = F, mfrow = c(3,1))
  dev.off()
}
  
```


## Treatment Comparison 

### Load data
```{r}
load("../../out/EstData/est_compare_vars_AR.RData") 
samp_names <- paste0("sampAR", sects)
for (i in 1:length(file_names)){
  load(file_names[[i]])
  assign(paste0(samp_names[i]), samples)
}
rm(samples, i)
samples_ls <- list("sampARC" = sampARC, "sampARS" = sampARS, "sampARSh" = sampARSh)
param_names <- c("mu_alpha", "delta_alpha", "mu_rho", "delta_rho",
                 "sigma_alpha_s", "sigma_alpha_m", "sigma_rho_s", "sigma_rho_m")

```


### Parameters
```{r}
comp_parameters <- array(NA, dim = c(length(param_names), length(samples_ls)), 
                              dimnames = list(c(param_names), c(names(samples_ls))))
for (p in param_names){
  for (s in 1:length(samples_ls)){
    comp_parameters[p, s] <- MPD(samples_ls[[s]]$BUGSoutput$sims.list[[p]])
  }
}
comp_parameters
```
### PosteriorXPrior distributions: ALPHA and RHO differences (delta)

```{r}
pdf(file = "../../out/AR_comp_postxprior.pdf")
par(mfrow=c(2,1))
colors <- c("black", "red", "blue", "green")
mpd_a <- c(round(comp_parameters[2,1:3], digits = 3))
plot(density(rnorm(1000, 0, 4)), col = colors[1], ylim = c(0,0.25), main = "delta_alpha")
lines(density(sampARC$BUGSoutput$sims.list$delta_alpha), col = colors[2])
lines(density(sampARS$BUGSoutput$sims.list$delta_alpha), col = colors[3])
lines(density(sampARSh$BUGSoutput$sims.list$delta_alpha), col = colors[4])
legend("topright", fill = colors, 
       legend = c("prior (mu = 0)", sprintf("sect: %s (%s)", sects, mpd_a)))

mpd_r <- c(round(comp_parameters[4,], digits = 3))
plot(density(rnorm(1000, 0, 0.5)), col = colors[1], ylim = c(0,2.5), main = "delta_rho")
lines(density(sampARC$BUGSoutput$sims.list$delta_rho), col = colors[2])
lines(density(sampARS$BUGSoutput$sims.list$delta_rho), col = colors[3])
lines(density(sampARSh$BUGSoutput$sims.list$delta_rho), col = colors[4])
legend("topright", fill = colors, 
       legend = c("prior (mu = 0)", sprintf("sect: %s (%s)", sects, mpd_r)))
dev.off()
```


### PosteriorXPrior distributions: ALPHA (mu) - for each sect 

```{r}
pdf(file = "../../out/AR_comp_alpha_dist.pdf")
par(mfrow = c(3,1))
colors <- c("black", "red", "blue")
mpd_c <- c(comp_parameters[1,1], comp_parameters[1,1] + comp_parameters[2,1], 
           comp_parameters[1,1] - comp_parameters[2,1])
names(mpd_c) <- c("sect_mu", "same_mu", "mixed_mu")
plot(density(sampARC$BUGSoutput$sims.list$mu_alpha), col = colors[1], main = "C - Mu alpha")
lines(density(sampARC$BUGSoutput$sims.list$mu_alpha + (sampARC$BUGSoutput$sims.list$delta_alpha/2)), 
      col = colors[2])
lines(density(sampARC$BUGSoutput$sims.list$mu_alpha - (sampARC$BUGSoutput$sims.list$delta_alpha/2)), 
      col = colors[3])
legend("topright", fill = colors, 
       legend = sprintf("%s - mpd %s", names(mpd_c), round(mpd_c, digits = 4)))

mpd_s <- c(comp_parameters[1,2], comp_parameters[1,2] + comp_parameters[2,2], 
           comp_parameters[1,2] - comp_parameters[2,2])
names(mpd_s) <- c("sect_mu", "same_mu", "mixed_mu")
plot(density(sampARS$BUGSoutput$sims.list$mu_alpha), col = colors[1], main = "S - Mu alpha")
lines(density(sampARS$BUGSoutput$sims.list$mu_alpha + (sampARS$BUGSoutput$sims.list$delta_alpha/2)), 
      col = colors[2])
lines(density(sampARS$BUGSoutput$sims.list$mu_alpha - (sampARS$BUGSoutput$sims.list$delta_alpha/2)), 
      col = colors[3])
legend("topright", fill = colors, 
       legend = sprintf("%s - mpd %s", names(mpd_s), round(mpd_s, digits = 4)))


mpd_sh <- c(comp_parameters[1,3], comp_parameters[1,3] + comp_parameters[2,3], 
           comp_parameters[1,3] - comp_parameters[2,3])
names(mpd_sh) <- c("sect_mu", "same_mu", "mixed_mu")
plot(density(sampARSh$BUGSoutput$sims.list$mu_alpha), col = colors[1], main = "Sh - Mu alpha")
lines(density(sampARSh$BUGSoutput$sims.list$mu_alpha + (sampARSh$BUGSoutput$sims.list$delta_alpha/2)), 
      col = colors[2])
lines(density(sampARSh$BUGSoutput$sims.list$mu_alpha - (sampARSh$BUGSoutput$sims.list$delta_alpha/2)), 
      col = colors[3])
legend("topright", fill = colors, 
       legend = sprintf("%s - mpd %s", names(mpd_sh), round(mpd_sh, digits = 4)))
dev.off()
```

### PosteriorXPrior distributions: RHO (mu) - for each sect 
```{r}
pdf(file = "../../out/AR_comp_rho_dist.pdf")
par(mfrow = c(3,1))
colors <- c("black", "red", "blue")
mpd_c <- c(comp_parameters[3,1], comp_parameters[3,1] + comp_parameters[4,1], 
           comp_parameters[3,1] - comp_parameters[4,1])
names(mpd_c) <- c("sect_mu", "same_mu", "mixed_mu")
plot(density(sampARC$BUGSoutput$sims.list$mu_rho), 
     col = colors[1], main = "C - Mu rho")
lines(density(sampARC$BUGSoutput$sims.list$mu_rho + (sampARC$BUGSoutput$sims.list$delta_rho/2)), 
      col = colors[2])
lines(density(sampARC$BUGSoutput$sims.list$mu_rho - (sampARC$BUGSoutput$sims.list$delta_rho/2)), 
      col = colors[3])
legend("topleft", fill = colors, 
       legend = sprintf("%s - mpd %s", names(mpd_c), round(mpd_c, digits = 4)))

mpd_s <- c(comp_parameters[3,2], comp_parameters[3,2] + comp_parameters[4,2], 
           comp_parameters[3,2] - comp_parameters[4,2])
names(mpd_s) <- c("sect_mu", "same_mu", "mixed_mu")
plot(density(sampARS$BUGSoutput$sims.list$mu_rho), col = colors[1], main = "S - Mu rho")
lines(density(sampARS$BUGSoutput$sims.list$mu_rho + (sampARS$BUGSoutput$sims.list$delta_rho/2)), 
      col = colors[2])
lines(density(sampARS$BUGSoutput$sims.list$mu_rho - (sampARS$BUGSoutput$sims.list$delta_rho/2)), 
      col = colors[3])
legend("topleft", fill = colors, 
       legend = sprintf("%s - mpd %s", names(mpd_s), round(mpd_s, digits = 4)))


mpd_sh <- c(comp_parameters[3,3], comp_parameters[3,3] + comp_parameters[4,3], 
           comp_parameters[3,3] - comp_parameters[4,3])
names(mpd_sh) <- c("sect_mu", "same_mu", "mixed_mu")
plot(density(sampARSh$BUGSoutput$sims.list$mu_rho), col = colors[1], main = "Sh - Mu rho")
lines(density(sampARSh$BUGSoutput$sims.list$mu_rho + (sampARSh$BUGSoutput$sims.list$delta_rho/2)), 
      col = colors[2])
lines(density(sampARSh$BUGSoutput$sims.list$mu_rho - (sampARSh$BUGSoutput$sims.list$delta_rho/2)), 
      col = colors[3])
legend("topleft", fill = colors, 
       legend = sprintf("%s - mpd %s", names(mpd_sh), round(mpd_sh, digits = 4)))
dev.off()
```


### Summaries 
```{r}
print("Christian Comparison")
sampARC
print("Sunni Comparison")
sampARS
print("Shia Compariosn")
sampARSh

#save to folder
folder_path <- "../../out/posterior_dist_summaries/m_AR_comp_"
for (i in 1:length(samples_ls)){
  path <- str_c(folder_path, sprintf("%s.csv", sects[i]))
  write.csv((samples_ls[[i]]$BUGSoutput$summary), file = path)
}
```

### Create dataframe with means and 95% CIS for plotting
```{r}
ARs_sum <- as.data.frame(round(sampARS$BUGSoutput$summary, digits = 3))
ARs_sum$var <- rownames(ARs_sum)
ARs_sum <- ARs_sum[c(1:2,4:9),c(1,3,5,7,8:10)]
ARs_sum$sect <- "Sunni" 

ARc_sum <- as.data.frame(round(sampARC$BUGSoutput$summary, digits = 3))
ARc_sum$var <- rownames(ARc_sum)
ARc_sum <- ARc_sum[c(1:2,4:9),c(1,3,5,7,8:10)]
ARc_sum$sect <- "Christian" 

ARsh_sum <- as.data.frame(round(sampARSh$BUGSoutput$summary, digits = 3))

ARsh_sum$var <- rownames(ARsh_sum)
ARsh_sum <- ARsh_sum[c(1:2,4:9), c(1,3,5,7,8:10)]
ARsh_sum$sect <- "Shia" 

AR_summary <- rbind(ARc_sum, ARs_sum, ARsh_sum)

ARsh_sum

```


```{r}

ggplot(data = AR_summary, aes(x = mean, y = sect)) + 
  geom_segment(aes(x = `2.5%`, xend = `97.5%`, yend = sect)) + 
  geom_point() + 
  facet_wrap(vars(var) , scales = "free", nrow = 4)+
  xlab("")+ylab("")+
  theme_minimal()

ggsave("../../out/AR_summary_plot.png")
```

### Traceplots
```{r}
traceplot(sampARC, ask = F)
traceplot(sampARS, ask = F)
traceplot(sampARSh, ask = F)

folder_path <-  "../../out/traceplots/m_AR_comp_"

for (i in 1:length(samples_ls)){
  path <- str_c(folder_path, sprintf("%s.pdf", sects[i]))
  pdf(file = path)
  traceplot(samples_ls[[i]], ask = F, mfrow = c(3,1))
  dev.off()
}
```



