# Posterior Predictive Checks Model-A: Public Goods Game

```{r}
install.packages("pacman")
set.seed(42)
pacman::p_load(R2jags, parallel, polspline, tidyverse, ggplot2)
setwd("/work/LauraGivskovRahbek#6659/decision_making_exam24/src/model_A")
source("../utils.R")
```


## Parameter Estimation (per group)
### Load data and vars
Each Combination of Sect and Treatment (6 groups)

```{r}
load("../../out/EstData/est_vars_A.RData") 
samp_names <- paste0("samp", SeTr)
for (i in 1:length(file_names)){
  load(file_names[[i]])
  assign(paste0(samp_names[i]), samples)
}
samples_ls <- list("sampC_0" = sampC_0, "sampC_1" = sampC_1, "sampS_0" = sampS_0, 
                   "sampS_1" = sampS_1, "sampSh_0" = sampSh_0, "sampSh_1" = sampSh_1)
param_names <- c("mu_alpha", "sigma_alpha")
```

### Estimated Parameters

```{r}
estimated_parameters <- array(NA, dim = c(length(param_names), length(samples_ls)), 
                              dimnames = list(c(param_names), c(names(samples_ls))))
for (p in param_names){
  for (s in 1:length(samples_ls)){
    estimated_parameters[p, s] <- MPD(samples_ls[[s]]$BUGSoutput$sims.list[[p]])
  }
}
estimated_parameters
```

### Prior distributions for SECTxTREATMENT
```{r}
par(mfrow = c(2,2))
plot(density(rgamma(1000, 2.6, 0.4)), xlim = c(0.001, 10), main = "Prior: Mu Alpha")
plot(density(rnorm(1000, 1, 2)), xlim = c(0.001, 10), main = "Prior: Sigma Alpha")
```


###Posterior Distributions for SECTxTREATMENT 

```{r}
pdf(file = "../../out/A_est_posterior.pdf")

par(mfrow = c(3,3))
for (p in param_names){
  for (s in 1:length(samples_ls)){
    plot(density(samples_ls[[s]]$BUGSoutput$sims.list[[p]]), 
         main = paste(p, samp_names[s], sep = " - ") )
  }
}
dev.off()
```


### Summary Tables (SECTxTREATMENT)
```{r}
print("Christian same-sect")
sampC_0
print("Christian mixed-sect")
sampC_1
print("Sunni same-sect")
sampS_0
print("Sunni same-sect")
sampS_1
print("Shia same-sect")
sampSh_0
print("Shia same-sect")
sampSh_1

#save to folder
folder_path <- "../../out/posterior_dist_summaries/m_A_est_"
for (i in 1:length(samples_ls)){
  path <- str_c(folder_path, sprintf("%s.csv", SeTr[i]))
  write.csv((samples_ls[[i]]$BUGSoutput$summary), file = path)
}
```


### Traceplots
```{r}

folder_path <-  "../../out/traceplots/m_A_est_"

for (i in 1:length(samples_ls)){
  path <- str_c(folder_path, sprintf("%s.pdf", SeTr[i]))
  pdf(file = path)
  traceplot(samples_ls[[i]], ask = F, mfrow = c(3,1))
  dev.off()
}
```



## Treatment Comparison 

### Load data
```{r}
load("../../out/EstData/est_compare_vars_A.RData") 
samp_names <- paste0("sampA", sects)
for (i in 1:length(file_names)){
  load(file_names[[i]])
  assign(paste0(samp_names[i]), samples)
}
rm(samples, i)
samples_ls <- list("sampAC" = sampAC, "sampAS" = sampAS, "sampASh" = sampASh)
param_names <- c("mu_alpha", "delta_alpha", "sigma_alpha_s", "sigma_alpha_m")

```


### Parameters
```{r}
comp_parameters <- array(NA, dim = c(length(param_names), length(samples_ls)), 
                              dimnames = list(c(param_names), c(names(samples_ls))))
for (p in param_names){
  for (s in 1:length(samples_ls)){
    comp_parameters[p, s] <- MPD(samples_ls[[s]]$BUGSoutput$sims.list[[p]])
  }
}
comp_parameters
```

### PosteriorXPrior distributions: ALPHA differences (delta)
```{r}
pdf(file = "../../out/A_comp_postxprior.pdf")

colors <- c("black", "red", "blue", "green")
mpd_a <- c(round(comp_parameters[2,1:3], digits = 3))
plot(density(rnorm(1000, 0, 4)), col = colors[1], 
     ylim = c(0,0.3), main = "delta_alpha")
lines(density(sampAC$BUGSoutput$sims.list$delta_alpha), col = colors[2])
lines(density(sampAS$BUGSoutput$sims.list$delta_alpha), col = colors[3])
lines(density(sampASh$BUGSoutput$sims.list$delta_alpha), col = colors[4])
legend("topright", fill = colors, 
       legend = c("prior (mu = 0)", sprintf("sect: %s (%s)", sects, mpd_a)))
dev.off()
```


### PosteriorXPrior distributions: ALPHA (mu) - for each sect 
```{r}
pdf(file = "../../out/A_comp_alpha_dist.pdf")
par(mfrow = c(3,1))
colors <- c("black", "red", "blue")
mpd_c <- c(comp_parameters[1,1], comp_parameters[1,1] + comp_parameters[2,1], 
           comp_parameters[1,1] - comp_parameters[2,1])
names(mpd_c) <- c("sect_mu", "same_mu", "mixed_mu")
plot(density(sampAC$BUGSoutput$sims.list$mu_alpha), col = colors[1], main = "C - Mu alpha")
lines(density(sampAC$BUGSoutput$sims.list$mu_alpha + (sampAC$BUGSoutput$sims.list$delta_alpha/2)), 
      col = colors[2])
lines(density(sampAC$BUGSoutput$sims.list$mu_alpha - (sampAC$BUGSoutput$sims.list$delta_alpha/2)), 
      col = colors[3])
legend("topright", fill = colors, legend = mpd_c)

mpd_s <- c(comp_parameters[1,2], comp_parameters[1,2] + comp_parameters[2,2], 
           comp_parameters[1,2] - comp_parameters[2,2])
names(mpd_s) <- c("sect_mu", "same_mu", "mixed_mu")
plot(density(sampAS$BUGSoutput$sims.list$mu_alpha), col = colors[1], main = "S - Mu alpha")
lines(density(sampAS$BUGSoutput$sims.list$mu_alpha + (sampAS$BUGSoutput$sims.list$delta_alpha/2)), 
      col = colors[2])
lines(density(sampAS$BUGSoutput$sims.list$mu_alpha - (sampAS$BUGSoutput$sims.list$delta_alpha/2)), 
      col = colors[3])
legend("topright", fill = colors, legend = mpd_s)


mpd_sh <- c(comp_parameters[1,3], comp_parameters[1,3] + comp_parameters[2,3], 
           comp_parameters[1,3] - comp_parameters[2,3])
names(mpd_sh) <- c("sect_mu", "same_mu", "mixed_mu")
plot(density(sampASh$BUGSoutput$sims.list$mu_alpha), col = colors[1], main = "Sh - Mu alpha")
lines(density(sampASh$BUGSoutput$sims.list$mu_alpha + (sampASh$BUGSoutput$sims.list$delta_alpha/2)), 
      col = colors[2])
lines(density(sampASh$BUGSoutput$sims.list$mu_alpha - (sampASh$BUGSoutput$sims.list$delta_alpha/2)), 
      col = colors[3])
legend("topright", fill = colors, legend = mpd_sh)
dev.off()
```



### Summary Tables (SECTxTREATMENT) compariosn
```{r}
print("Christian Comparison")
sampAC
print("Sunni Comparison")
sampAS
print("Shia Compariosn")
sampASh

#save to folder
folder_path <- "../../out/posterior_dist_summaries/m_A_comp_"
for (i in 1:length(samples_ls)){
  path <- str_c(folder_path, sprintf("%s.csv", sects[i]))
  write.csv((samples_ls[[i]]$BUGSoutput$summary), file = path)
}
```

### Create dataframe with means and 95% CIS for plotting
```{r}
As_sum <- as.data.frame(round(sampAS$BUGSoutput$summary, digits = 3))
As_sum$var <- rownames(As_sum)
As_sum <- As_sum[c(1,3:5),c(1,3,5,7,8:10)]
As_sum$sect <- "Sunni" 

Ac_sum <- as.data.frame(round(sampAC$BUGSoutput$summary, digits = 3))
Ac_sum$var <- rownames(Ac_sum)
Ac_sum <- Ac_sum[c(1,3:5),c(1,3,5,7,8:10)]
Ac_sum$sect <- "Christian" 

Ash_sum <- as.data.frame(round(sampASh$BUGSoutput$summary, digits = 3))

Ash_sum$var <- rownames(Ash_sum)
Ash_sum <- Ash_sum[c(1,3:5), c(1,3,5,7,8:10)]
Ash_sum$sect <- "Shia" 

A_summary <- rbind(Ac_sum, As_sum, Ash_sum)

As_sum

```

```{r}

ggplot(data = A_summary, aes(x = mean, y = sect)) + 
  geom_segment(aes(x = `2.5%`, xend = `97.5%`, yend = sect)) + 
  geom_point() + 
  facet_wrap(vars(var) , scales = "free", nrow = 4)+
  xlab("")+ylab("")+
  theme_minimal()
ggsave("../../out/A_summary_plot.png", width = 3.5, height = 4.32)

```

### Traceplots
```{r}
traceplot(sampAC, ask = F)
traceplot(sampAS, ask = F)
traceplot(sampASh, ask = F)

folder_path <-  "../../out/traceplots/m_A_comp_"

for (i in 1:length(samples_ls)){
  path <- str_c(folder_path, sprintf("%s.pdf", sects[i]))
  pdf(file = path)
  traceplot(samples_ls[[i]], ask = F, mfrow = c(3,1))
  dev.off()
}
```


